Mixed effect tweedie model in TMB

### 2019-04-14 analysis/tmb-sensor-explore/2-fit-temperature.Rmd

# 10-fold cross-validation

## All fixed slope models
```{r}
cv_args <- generate_cv_args (formula = list(
    temperature_c ~ 0 + as.factor(year) + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3),
    time_varying = list(NULL),
    ar1_fields = c(FALSE, TRUE), 
    include_spatial = c(FALSE,TRUE),
    n_knots = c(30,80,150)
  )

plan(multiprocess)
sdmTMB_cv_batch <- purrr::pmap(cv_args, sdmTMB_cv, data = d_trawl)
cv_args1 <- cv_args
cv_loglik <- c()
for (i in seq_len(nrow(cv_args1))) {
  cv_loglik[[i]] <- round(sdmTMB_cv_batch1[[i]]$sum_loglik, 1)
}
cv_args1$formula <- as.character(cv_args1$formula)
cv_args1$cv_loglik <- cv_loglik
View(cv_args1)
cv_args_notv <- as.data.frame(cv_args1) %>% select(., -time_varying)
glimpse(cv_args_notv)
write.csv(cv_args_notv, file="cv-all-non-time-varying.csv")
```

@@

plan(multiprocess)
sdmTMB_cv_batch <- purrr::pmap(cv_args, sdmTMB_cv, data = d_trawl)

cv_loglik <- c()
for (i in seq_len(nrow(cv_args))) {
  cv_loglik[[i]] <- c(sdmTMB_cv_batch[[i]]$sum_loglik)
}
cv_args2 <- cv_args
cv_args2$formula <- as.character(cv_args$formula)
cv_args2$time_varying <- as.character(cv_args$time_varying)
cv_args2$cv_loglik <- cv_loglik
glimpse(cv_args2)
cv_args_tv <- as.data.frame(cv_args2) 
write.csv(cv_args_tv, file="cv-all-time-varying.csv")
```

@@

## Plotting predictions

```{r}
predictions_nd <- predict(m_temp2_rw_nosp, newdata = qcs_grid)
#saveRDS(predictions3_rw_nd$data, file = "qcs-temp.rds")
```

```{r}
plot_map(predictions_nd$data, "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}
plot_map(predictions_nd$data, "est_fe") +
  ggtitle("Prediction (fixed effects only)") +
  scale_fill_viridis_c(trans = "sqrt")
```

```{r, eval=FALSE}
plot_map(predictions_nd$data, "est_re_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2()
```

```{r}
plot_map(predictions_nd$data, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()
```

########################
########################

Various candidate models

########################
########################

```{r}
spde <- make_spde(d_fit$X, d_fit$Y, n_knots = 100)
p <- plot_spde(spde)
p
```

```{r}
withheld_fe <- sample(d_trawl$fishing_event_id, size = round(nrow(d_trawl)*.2))
d_withheld <- filter(d_trawl, fishing_event_id %in% withheld_fe)
d_fit <- filter(d_trawl, !fishing_event_id %in% withheld_fe)

nrow(d_fit) # 3774
nrow(d_withheld) # 943
unique(d_withheld$year) 
unique(d_fit$year)
length(unique(d_fit$year))
```

Misc models
```{r}
temp2 <- sdmTMB_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
plot_cv_meshes(temp2)
sum(temp2$sum_loglik)

temp3 <- sdmTMB_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3$sum_loglik)

# allow slope with depth to vary through between years with a random walk
temp1_rw <- sdmTMB_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp1_rw$sum_loglik)

temp2_rw <- sdmTMB_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp2_rw$sum_loglik)

temp3_rw <- sdmTMB_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3_rw$sum_loglik)
```

```{r}
m_temp1 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + depth_scaled,
  time = "year", spde = spde, family = gaussian(link = "identity"), 
  ar1_fields = FALSE, include_spatial = FALSE, 
  silent = TRUE)

predictions <- predict(m_temp1)
predictions$data$residuals <- residuals(m_temp1)
cor(predictions$data$est, predictions$data$temperature_c)^2
aic(m_temp1)

m_temp1_nosp  <- m_temp1
```

AR1 fields no improvement in R^2
```{r, eval=FALSE}
m_temp1_ar1 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + depth_scaled,
  time = "year", spde = spde, family = gaussian(link = "identity"), 
  ar1_fields = TRUE, include_spatial = FALSE, 
  anisotropy = FALSE, 
  silent = TRUE)

predictions_ar1 <- predict(m_temp1_ar1)
predictions_ar1$data$residuals <- residuals(m_temp1_ar1)
cor(predictions_ar1$data$est, predictions_ar1$data$temperature_c)^2
aic(m_temp1_ar1)
```

Time-varying slope for depth, little imporvement for R^2
```{r}
m_temp1_rw <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year),   
  time_varying = ~ 0 + depth_scaled,
  ar1_fields = FALSE, include_spatial = FALSE, #these are defaults
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions1_rw <- predict(m_temp1_rw)
predictions1_rw$data$residuals <- residuals(m_temp1_rw)
cor(predictions1_rw$data$est, predictions1_rw$data$temperature_c)^2
aic(m_temp1_rw)
```

NO improvement
```{r, eval=FALSE}
m_temp1_rw_ar1 <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year),   
  time_varying = ~ 0 + depth_scaled,
  ar1_fields = TRUE, include_spatial = TRUE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions1_rw_ar1 <- predict(m_temp1_rw_ar1)
predictions1_rw_ar1$data$residuals <- residuals(m_temp1_rw_ar1)
cor(predictions1_rw_ar1$data$est, predictions1_rw_ar1$data$temperature_c)^2
aic(m_temp1_rw_ar1)
```

NO improvement
```{r, eval=FALSE}
m_temp1_st <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year) + depth_scaled,
  #time_varying =  ~ 0 + depth_scaled,
  include_spatial = TRUE, ar1_fields = FALSE, spatial_trend = TRUE, 
  # seems to be only config that converges
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions1_st <- predict(m_temp1_st)
predictions1_st$data$residuals <- residuals(m_temp1_st)
cor(predictions1_st$data$est, predictions1_st$data$temperature_c)^2 # 
aic(m_temp1_st)
```

Both time and space varying... doesn't improve R^2
```{r, eval=FALSE}
m_temp1_rw_st <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year), 
  time_varying =  ~ 0 + depth_scaled,
  include_spatial = TRUE, ar1_fields = FALSE, spatial_trend = TRUE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions1_rw_st <- predict(m_temp1_rw_st)
predictions1_rw_st$data$residuals <- residuals(m_temp1_rw_st)
cor(predictions1_rw_st$data$est, predictions1_rw_st$data$temperature_c)^2 # 
aic(m_temp1_rw_st)
```

What about polynomial response to depth?

```{r, eval=FALSE}
#d_trawl$depth2 <- (d_trawl$depth_scaled)^2
#d_trawl$depth3 <- (d_trawl$depth_scaled)^3

m_temp2 <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year) + depth_scaled + depth2,
  ar1_fields = FALSE, include_spatial = TRUE, #these are defaults
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions2 <- predict(m_temp2)
predictions2$data$residuals <- residuals(m_temp2)
cor(predictions2$data$est, predictions2$data$temperature_c)^2
aic(m_temp2)
```

```{r}
m_temp2_nosp <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year) + depth_scaled + depth2,
  ar1_fields = FALSE, include_spatial = FALSE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions2_nosp <- predict(m_temp2_nosp)
predictions2_nosp$data$residuals <- residuals(m_temp2_nosp)
cor(predictions2_nosp$data$est, predictions2_nosp$data$temperature_c)^2
aic(m_temp2_nosp)
```

```{r}
m_temp2_rw_nosp <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + depth_scaled + depth2,
  include_spatial = FALSE, ar1_fields = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions2_rw_nosp <- predict(m_temp2_rw_nosp)
predictions2_rw_nosp$data$residuals <- residuals(m_temp2_rw_nosp)
cor(predictions2_rw_nosp$data$est, predictions2_rw_nosp$data$temperature_c)^2
aic(m_temp2_rw_nosp)
```

NO improvement 
```{r, eval=FALSE}
m_temp2_st <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year), #+ poly(depth_scaled, 2),
  time_varying =  ~ 0 + poly(depth_scaled, 2),
  include_spatial = FALSE, ar1_fields = FALSE, spatial_trend = TRUE, 
  # seems to be only config that converges
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions2_st <- predict(m_temp2_st)
predictions2_st$data$residuals <- residuals(m_temp2_st)
cor(predictions2_st$data$est, predictions2_st$data$temperature_c)^2 # 
aic(m_temp2_st)
```

What about 3 order polynomial?
```{r, eval=FALSE}
m_temp3 <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year) + depth_scaled + depth2 + depth3,
  ar1_fields = FALSE, include_spatial = TRUE, #these are defaults
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions3 <- predict(m_temp3)
predictions3$data$residuals <- residuals(m_temp3)

cor(predictions3$data$est, predictions3$data$temperature_c)^2 # 
```

Slightly better without a fixed spatial field!
```{r}
m_temp3_nosp <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year) + depth_scaled + depth2 + depth3,
  ar1_fields = FALSE, include_spatial = FALSE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions3_nosp <- predict(m_temp3_nosp)
predictions3_nosp$data$residuals <- residuals(m_temp3_nosp)

cor(predictions3_nosp$data$est, predictions3_nosp$data$temperature_c)^2 # 
```

Better without AR1
```{r, eval=FALSE}
m_temp3_ar1 <- sdmTMB(d_fit, 
  temperature_c ~ 0 + as.factor(year) + depth_scaled + depth2 + depth3,
  ar1_fields = TRUE, include_spatial = FALSE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions3_ar1 <- predict(m_temp3_ar1)
predictions3_ar1$data$residuals <- residuals(m_temp3_ar1)

cor(predictions3_ar1$data$est, predictions3_ar1$data$temperature_c)^2 # 
```

```{r, eval=FALSE}
m_temp3_rw <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + depth_scaled + depth2 + depth3,
  ar1_fields = FALSE, include_spatial = TRUE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

Also better without fixed spatial field but not quite as good as 2nd order
```{r}
m_temp3_rw_nosp <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + depth_scaled + depth2 + depth3,
  include_spatial = FALSE, ar1_fields = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions3_rw_nosp <- predict(m_temp3_rw_nosp)
predictions3_rw_nosp$data$residuals <- residuals(m_temp3_rw_nosp)
cor(predictions3_rw_nosp$data$est, predictions3_rw_nosp$data$temperature_c)^2 # 
```

Not converging 
```{r, eval=FALSE}
m_temp3_st <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year), #+ poly(depth_scaled, 2),
  time_varying =  ~ 0 + depth_scaled + depth2 + depth3,
  include_spatial = FALSE, ar1_fields = FALSE, spatial_trend = TRUE, 
  # seems to be only config that converges
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

predictions3_st <- predict(m_temp3_st)
predictions3_st$data$residuals <- residuals(m_temp3_st)
cor(predictions3_st$data$est, predictions3_st$data$temperature_c)^2 # 
```

# Conclusion:

```{r}
# m_temp2_rw$model$par
# 2 * plogis(m_temp1$model$par[["ar1_phi"]]) - 1
# exp(m_temp2_rw$model$par[["ln_phi"]])

p_withheld1 <- predict(m_temp1_nosp, newdata = d_withheld)
cor(p_withheld1$data$est, p_withheld1$data$temperature_c)^2 # 0.87 in first 
```
```{r}
p_withheld1_rw <- predict(m_temp1_rw, newdata = d_withheld)
cor(p_withheld1_rw$data$est, p_withheld1_rw$data$temperature_c)^2 # 0.87 in first 
```

# 4
```{r}
p_withheld2 <- predict(m_temp2_nosp, newdata = d_withheld)
cor(p_withheld2$data$est, p_withheld2$data$temperature_c)^2 # 
```

# 2
```{r}
p_withheld2_rw <- predict(m_temp2_rw_nosp, newdata = d_withheld)
cor(p_withheld2_rw$data$est, p_withheld2_rw$data$temperature_c)^2 # 
```

# 3
```{r}
p_withheld3 <- predict(m_temp3_nosp, newdata = d_withheld)
cor(p_withheld3$data$est, p_withheld3$data$temperature_c)^2 # 0.87
```

# 1
```{r}
p_withheld3_rw <- predict(m_temp3_rw_nosp, newdata = d_withheld)
cor(p_withheld3_rw$data$est, p_withheld3_rw$data$temperature_c)^2 # 0.87
```

```{r}
ggplot(p_withheld3_rw$data, aes(temperature_c,est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,15) +
  ylim(3,15) +
  geom_abline()
```

Residual plots:
```{r}
ggplot(predictions3_rw_nosp$data, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions2_rw_nosp$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions2_rw_nosp$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth()
```

```{r}
ggplot(predictions3_rw_nosp$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth()
```

# there is probably a problem with doing this... but need to figure out how to add poly args to predict function
```{r eval=FALSE}
m_temp2_rw_poly <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled,2),
  include_spatial = FALSE, ar1_fields = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)
```

>>>>

# 10-fold cross-validation 
#FIXME: need to extract information on whether or not models converge
## All fixed slope models
```{r}
cv_args <- generate_cv_args (formula = list(
    temperature_c ~ 0 + as.factor(year) + depth_scaled,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
    temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3),
    time_varying = list(NULL),
    ar1_fields = c(FALSE, TRUE), 
    include_spatial = c(FALSE,TRUE),
    n_knots = c(30,80,150)
  )

plan(multiprocess)
sdmTMB_cv_batch1 <- purrr::pmap(cv_args, sdmTMB_cv, data = d_trawl)
cv_args1 <- cv_args
cv_loglik <- c()
for (i in seq_len(nrow(cv_args1))) {
  cv_loglik[[i]] <- round(sdmTMB_cv_batch1[[i]]$sum_loglik, 1)
}
cv_args1$formula <- as.character(cv_args1$formula)
cv_args1$cv_loglik <- cv_loglik
cv_args_notv <- as.data.frame(cv_args1) %>% select(., -time_varying)
# View(cv_args_notv)
# write.csv(cv_args_notv, file = "cv-all-non-time-varying.csv")
# saveRDS(sdmTMB_cv_batch1, file = "cv-all-non-time-varying.rds")
glimpse(cv_args_notv)
```

@@

plan(multiprocess)
sdmTMB_cv_batch <- purrr::pmap(cv_args, sdmTMB_cv, data = d_trawl)
cv_args2 <- cv_args
cv_args2$cv_loglik <- c()
for (i in seq_len(nrow(cv_args))) {
  cv_args2$cv_loglik[[i]] <- c(sdmTMB_cv_batch[[i]]$sum_loglik)
}
cv_args2$formula <- as.character(cv_args$formula)
cv_args2$time_varying <- as.character(cv_args$time_varying)
cv_args_tv <- as.data.frame(cv_args2) 
# View(cv_args_tv)
# write.csv(cv_args_tv, file = "cv-all-time-varying.csv")
# saveRDS(sdmTMB_cv_batch, file = "cv-all-time-varying.rds")
glimpse(cv_args_tv)
```

## vary n_knots for top model
```{r}
cv_args_knots <- generate_cv_args (formula = list(
    temperature_c ~ 0 + as.factor(year)),
    time_varying = list(
    ~ 0 + depth_scaled + depth_scaled2,
    ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3),
    ar1_fields = c(FALSE,TRUE), 
    include_spatial = c(FALSE,TRUE),
    n_knots = c(60,90,110,130,160)
    )

plan(multiprocess)
sdmTMB_cv_knots2 <- purrr::pmap(cv_args_knots, sdmTMB_cv, data = d_trawl)
cv_args3 <- cv_args_knots
cv_args3$cv_loglik <- c()
for (i in seq_len(nrow(cv_args3))) {
  cv_args3$cv_loglik[[i]] <- c(sdmTMB_cv_knots2[[i]]$sum_loglik)
}
cv_args3$formula <- as.character(cv_args3$formula)
cv_args3$time_varying <- as.character(cv_args3$time_varying)
cv_args_knots2 <- as.data.frame(cv_args3) 
# View(cv_args_knots2)
# write.csv(cv_args_knots2, file = "cv-varying_knots2.csv")
# saveRDS(sdmTMB_cv_knots2, file = "cv-varying_knots2.rds")
glimpse(cv_args_knots2)
```

Load saved batches:
```{r}
non_time_varying_batch <- readRDS(file = "cv-all-non-time-varying.rds")
time_varying_batch <- readRDS(file = "cv-all-time-varying.rds")
knot_varying_batch <- readRDS(file = "cv-varying_knots.rds")
knot_varying_batch2 <- readRDS(file = "cv-varying_knots2.rds")
```

Current top model
```{r}
plan(multiprocess)
temp3_rw <- sdmTMB_cv(data = d_trawl, n_knots = 130, x = "X", y ="Y", k_folds = 10, 
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = TRUE, include_spatial = TRUE)
temp3_rw$models
sum(temp3_rw$sum_loglik)
```

```{r}
spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 130)
plot_spde(spde)
```

```{r}
m_temp3_rw <- sdmTMB(d_trawl,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
  ar1_fields = TRUE, include_spatial = TRUE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

Residual plots:
```{r}
ggplot(predictions3_rw$data, aes(est, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions3_rw$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~year)
```

```{r}
ggplot(predictions3_rw$data, aes(depth_scaled, residuals)) +
  geom_point() +
  geom_smooth()
```

@@

## Plotting predictions
```{r}
qcs_grid$depth_scaled3 <- (qcs_grid$depth_scaled)^3
predictions_nd <- predict(m_temp3_rw, newdata = qcs_grid)
#saveRDS(predictions3_rw_nd$data, file = "qcs-temp.rds")
```

```{r}
plot_map_raster(predictions_nd$data, "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}
plot_map_raster(predictions_nd$data, "est_fe") +
  ggtitle("Prediction (fixed effects only)") +
  scale_fill_viridis_c(trans = "sqrt")
```

```{r, eval=FALSE}
plot_map_raster(predictions_nd$data, "est_re_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2()
```

```{r}
plot_map_raster(predictions_nd$data, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()
```

```{r}
ggplot(predictions3_rw$data, aes(temperature_c, est)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  xlim(3,15) +
  ylim(3,15) +
  geom_abline()
```
